Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-08-31 grove-paper.tex
Revise figure and diagram for multi-parent conflict section

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{+}_{2}$" [> "left", > "19"'] -> {
    "$\texttt{var(x)}_{2}$" [> "left", > "19"'],
    {}
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Multi-parent-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{+}_{2}$" [> "left", > "19"'],
   "$\texttt{var(x)}_{2}$" [> "left", > "19"']
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Multi-parent-a} after Alice ... TODO}
\label{fig:Multi-parent-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{+}_{2}$" [> "left", > "19"'] -> {
    {},
    "$\texttt{var(x)}_{2}$" [> "right", > "19"']
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Multi-child-a} after Bob ... TODO}
\label{fig:Multi-parent-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  a/{$\texttt{+}_{8}$} [> "root", > "7"'] -> {
   "$\texttt{+}_{2}$" [> "left", > "19"'] ->["right", "19"'] {
    {},
    b/"$\texttt{var(x)}_{2}$"
   },
   {}
  }
 },
 a ->["right", "27"'] b
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Multi-parent-b} with \autoref{fig:Multi-parent-c}}
\label{fig:Multi-parent-d}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-parent conflicts}
\label{fig:Multi-parent}
\end{figure}

@@

TODO: edge and vertex numbers

@@

An example of this is shown in \autoref{fig:Multi-parent},
which starts with the top graph, which represents the expression~\texttt{\hole + (\hole + x)}.
Suppose Alice moves the variable~\texttt{x} to the left-most hole.
This results in the left graph, which represents the expression~\texttt{x + (\hole + \hole)}.
At the same time, suppose Bob moves the variable~\texttt{x} to the right-most hole.
This results in the right graph, which represents the expression~\texttt{\hole + (x + \hole)}.
In both cases, these edits are achieved with one edge delete and one edge add.
Alice deletes edge TODO and adds edge TODO, while Bob deletes edge TODO and adds edge TODO.
As explained in Subsection~TODO:REF, deletes are idempotent so both Alice and Bob deleting
edge TODO is not a problem.
However, both edge TODO (added by Alice) and edge TODO (added by Bob) point to the same vertex.
This generates the bottom graph, in which vertex TODO as two parents pointing to it.
We call this situation a multi-parent conflict.

TODO: plus(x, \hole) that both Alice and Bob move the "x" to the right -> This results in two edges from plus to x.

>>>>

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{+}_{24}$" [> "left", > "23"'] -> {
    "$\texttt{var(x)}_{26}$" [> "left", > "25"'],
    {}
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Multi-parent-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{+}_{24}$" [> "left", > "23"'],
   "$\texttt{var(x)}_{26}$" [> "right", > "27"']
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Multi-parent-a} after Alice ... TODO}
\label{fig:Multi-parent-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{+}_{24}$" [> "left", > "23"'] -> {
    {},
    "$\texttt{var(x)}_{26}$" [> "right", > "29"']
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Multi-child-a} after Bob ... TODO}
\label{fig:Multi-parent-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  a/{$\texttt{+}_{8}$} [> "root", > "7"'] -> {
   "$\texttt{+}_{24}$" [> "left", > "23"'] ->["right", "29"'] {
    {},
    b/"$\texttt{var(x)}_{26}$"
   },
   {}
  }
 },
 a ->["right", "27"'] b
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Multi-parent-b} with \autoref{fig:Multi-parent-c}}
\label{fig:Multi-parent-d}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-parent conflicts}
\label{fig:Multi-parent}
\end{figure}

@@

@@

An example of this is shown in \autoref{fig:Multi-parent}.
\autoref{fig:Multi-parent-a} shows the graph after Alice and Bob have made some more edits,
and Alice and Bob's editors are synchronized with each other.
This graph represents the expression~\texttt{(x + \hole{}) + \hole{})}.
Alice moves the variable~\texttt{x} to the left-most hole,
while Bob moves it to the right-most hole.
This results in the graphs in \autoref{fig:Multi-parent-b} and \autoref{fig:Multi-parent-c},
which represent respectively the expression~\texttt{(\hole{} + \hole{}) + x} for Alice
and the expression~\texttt{(\hole{} + x) + \hole{}} for Bob.
In both cases, these edits are achieved with one edge delete and one edge add.
Alice deletes \edge{25} and adds \edge{27}, while Bob deletes \edge{25} and adds edge \edge{29}.
As explained in Subsection~TODO:REF, deletes are idempotent so Alice and Bob both deleting \edge{25} is not a problem.
However, both \edge{27} (added by Alice) and edge \edge{29} (added by Bob) point to the same vertex.
This generates the bottom graph, in which \vertex{26} as two parents pointing to it.
We call this situation a multi-parent conflict.
